\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-05 3-advanced.Rmd
add caption for figure 5

```{r illu-interactive, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "demon interactivity"}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.004.png"))
```

>>>>

```{r illu-interactive, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "An illustration of the data model under interactive graphics with cubble. The line plot and map is made separately with the long and nested cubble. When a station is selected on the map (left), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (middle) and update the line plot (right)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.004.png"))
```

### 2022-02-05 main.tex
small fix
add caption for figure 5

\Keywords{spatio-temporal data, \proglang{R}, climate data}
\Plainkeywords{spatio-temporal data, R, climate data}

@@

@@

\caption[demon interactivity]{demon interactivity}\label{fig:illu-interactive}
\end{figure}
\end{CodeChunk}

>>>>

\Keywords{spatio temporal, \proglang{R}, climate weather station, data
analysis}
\Plainkeywords{spatio temporal, R, climate weather station, data
analysis}

@@

      Nicolas Langrené\\
    BNU-HKBU United International College\\
    2000 Jintong Road, Tangjiawan, Zhuhai, Guangdong Province, China\\
  E-mail: \href{mailto:nicolas@langrene.com}{\nolinkurl{nicolas@langrene.com}}\\

@@

\caption[An illustration of the data model under interactive graphics with cubble]{An illustration of the data model under interactive graphics with cubble. The line plot and map is made separately with the long and nested cubble. When a station is selected on the map (left), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (middle) and update the line plot (right).}\label{fig:illu-interactive}
\end{figure}
\end{CodeChunk}
